---
title: "Report"
author: "yawei wang"
date: "9/23/2020"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

Select one sample A, one sample B, one sample C and one sample D.Then simulate their read counts by Binom(n,0.5), Binom(n,0.25),Binom(n,0.125),Binom(n,0.05),Binom(n,0.01) and get a new dataset. Use upper quantile, median, quantile, TMM, Deseq and new method to do normalization.  Then calculate the spearman correlation with TaqMan qRT-PCR data and get results. At last, make barplots to compare the performance of different normalization methods. 





```{r, load-package}
library(ggplot2)
library(dplyr)
library(tidyr)
```

```{r}

sampleA<-read.csv("./sampleA.csv")
sampleB<-read.csv("./sampleB.csv")
sampleC<-read.csv("./sampleC.csv")
sampleD<-read.csv("./sampleD.csv")
```


```{r }
knitr::opts_chunk$set(echo = TRUE)

gathercol<-names(sampleA)[-1]
a<-sampleA %>% gather(pa,measurment,gathercol)
a$measurment<-as.numeric(a$measurment)
pa<-ggplot(data = a,aes(pa,measurment,fill=method)) 
paa<-pa+geom_bar(stat="identity", position=position_dodge()) + 
  scale_y_continuous(limits=c(0,0.88),breaks=seq(0.80,0.88,0.02))+labs(title = "sampleA")+coord_cartesian(ylim=c(0.7369766,0.88))
paa
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r}

gathercol<-names(sampleB)[-1]
b<-sampleB %>% gather(pb,measurment,gathercol)
b$measurment<-as.numeric(b$measurment)
pb<-ggplot(data = b,aes(pb,measurment,fill=method)) 
pbb<-pb+geom_bar(stat="identity", position=position_dodge()) + 
  scale_y_continuous(limits=c(0,0.88),breaks=seq(0.32,0.88,0.02))+labs(title = "sampleB")+coord_cartesian(ylim=c(0.34,0.88))
pbb

```
```{r}

gathercol<-names(sampleC)[-1]
c<-sampleC %>% gather(pc,measurment,gathercol)
c$measurment<-as.numeric(c$measurment)
pc<-ggplot(data = c,aes(pc,measurment,fill=method)) 
pcc<-pc+geom_bar(stat="identity", position=position_dodge()) + 
  scale_y_continuous(limits=c(0,0.88),breaks=seq(0.32,0.88,0.01))+labs(title = "sampleC")+coord_cartesian(ylim=c(0.71,0.85))
pcc
```
```{r}

gathercol<-names(sampleD)[-1]
d<-sampleD %>% gather(pd,measurment,gathercol)
d$measurment<-as.numeric(d$measurment)
pd<-ggplot(data = d,aes(pd,measurment,fill=method)) 
pdd<-pd+geom_bar(stat="identity", position=position_dodge()) + 
  scale_y_continuous(limits=c(0,0.88),breaks=seq(0.32,0.88,0.01))+labs(title = "sampleD")+coord_cartesian(ylim=c(0.55,0.85))
pdd
```


as the results shown, the new methods for normalization does not have a obvious distinct advantage.

```{r}

library("Rmisc")
library("plyr")
library("lattice")
final<-multiplot(paa, pbb, pcc, pdd, cols=1)
final
getwd()
devtools::session_info()



```

